%
% Shipping.tex
% Shipping and Receiving
%
% Aleph Objects Operations Manual
%
% Copyright (C) 2014 Aleph Objects, Inc.
%
% This document is licensed under the Creative Commons Attribution 4.0
% International Public License (CC BY-SA 4.0) by Aleph Objects, Inc.
%

\section{Serial Numbers}
\subsection{Updating Serial Numbers in Delivery Order}

Serial numbers can be entered only in a draft Delivery Order. 
\begin{enumerate}
\item For each line in the delivery order, click on the “Split in Serial Number” button on the line.

\item Click on Add an Item in the popup that opens and key in the serial number.

Enter serial number and quantity for each number. Typically, in Aleph Objects case, the quantity will be 1 for each serial number.

In the above example, the quantity is defined at 2. So, enter two serial numbers on two separate lines.
\item When serial number is entered, choose the “Create and Edit” option after keying in the serial number. This will bring up a popup as shown below.

Enter internal reference, prefix information if required.
Do not enter revision number or stock moves in this popup.
Save the serial number.
\item Repeat the process for each line in the delivery order with a product that requires serial number association.
\end{enumerate}

\section{Delivery}

\section{Inventory}
OpenERP ---> Warehouse

\subsection{Receiving}

OpenERP ---> Warehouse ---> Receive/Deliver By Orders ---> Incoming Shipments

\subsection{Moves}

OpenERP ---> Warehouse ---> Receive/Deliver By Orders ---> Internal Moves

\section{Export Compliance}
If you are unsure, don't ship. If we don't have the answer internally, contact
Denver office of export.gov.

\section{Products}

OpenERP ---> Warehouse ---> Products ---> Products

\section{Harmonized codes}
Every Product we sell must have a harmonized code listed. We are using the
USA's Schedule B.

\section{Country of origin}
We need to know the country of origin of every product we sell.

\section{NAFTA}
We can get most of our Products into Canada and Mexico duty free under the
North American Free Trade Agreement. Our printers and most of our parts
qualify.

