%
% IT.
% Information Technology
%
% Aleph Objects Operations Manual
%
% Copyright (C) 2014, 2015 Aleph Objects, Inc.
%
% This document is licensed under the Creative Commons Attribution 4.0
% International Public License (CC BY-SA 4.0) by Aleph Objects, Inc.
%

\section{Server Daemons}
These are the server daemons used to drive the enterprise.

\subsection{\href{http://sourceforge.net/projects/acpid2/}{ACPID}}
Monitors ACPI events. Runs on nearly all servers and workstations.

\subsection{\href{http://httpd.apache.org/}{Apache}}
Web daemon, used on many servers.

\subsection{\href{http://www.asterisk.org}{Asterisk}}
Telephone server. DIDs (incoming), termination (outgoing), forwarding of calls, conferencing,
voicemail, XMPP.

\subsection{\href{https://github.com/tummy-dot-com/tummy-backup}{Backups}}
tummy-backup backup server.

\subsection{\href{http://www.isc.org/}{BIND}}
Nameserver used for caching.

\subsection{\href{http://www.botqueue.org/}{botqueue}}
Print queue manager.

\subsection{\href{http://www.debian.org/}{buildd}}
Build service for compiling Debian packages.

\subsection{\href{http://www.calendarserver.org/}{Calendar Server}}
Calendar (CalDAV) and contacts (CardDAV) server. CalDAV is used with mobile
phones and icedove. No group calendars. CardDav is unused. Uses python-twisted.

Needs to be connected to or replaced by LDAP.

\subsection{\href{http://ftp.isc.org/isc/cron/}{cron}}
Scheduled triggering of applications (cf. at).

\subsection{\href{http://dnsmasq.org/}{DHCP}}
dnsmasq DHCP for 350+ hosts.

\subsection{\href{http://dnsmasq.org/}{DNS}}
dnsmasq DNS caching.

\subsection{\href{http://dnsmasq.org/}{Dovecot}}
IMAP mail services. Employees check their mail via the
IMAP server, typically using icedove or aomail (roundcube using IMAP).

\subsection{\href{http://www.drupal.org}{Drupal}}
Main LulzBot site.

Used with \href{http://www.ubercart.org/}{UberCart}.
Migrating to Drupal Commerce.

\subsection{\href{http://www.exim.org/}{exim}}
SMTP outgoing mail server, used by default in Debian. Used by some servers.

\subsection{\href{http://www.openbsd.org/faq/pf/}{Firewalls}}
OpenBSD's PF, authpf, Linux's iptables.

\subsection{\href{http://www.fail2ban.org/}{fail2ban}}
Block out scripts, bots, crackers, and network noise on servers.

\subsection{\href{http://www.debian.org/}{Init}}
Init, woo!

\subsection{md RAID}
Linux RAID, md, mdadm.

\subsection{\href{http://www.mediawiki.org/}{Mediawiki}}
Test/development server for customer support.

\subsection{\href{http://www.memcached.org/}{memcached}}
Used to speed up websites, such as Drupal.

\subsection{\href{http://motion.sf.net}{Motion}}
Motion detection for video camera system. Cameras are aggregated
using \href{https://bitbucket.org/ccrisan/motioneye/wiki/Home}{motionEye}.

\subsection{\href{http://munin-monitoring.org/}{Munin}}
Network graphing.

\subsection{\href{http://www.mysql.org/}{MySQL}}
Used on many servers for a database.

\subsection{\href{http://support.ntp.org/}{NTP}}
Syncs time on every server and workstation.

\subsection{\href{http://www.odoo.com/}{Odoo}}
Development ERP server, next generation of OpenERP.

\subsection{\href{http://www.openerp.org/}{OpenERP}}
ERP server.

\subsection{\href{http://www.openldap.org/}{OpenLDAP}}
LDAP server. Running, but not actively used. Daemon is slapd.

\subsection{\href{http://www.openssh.com/}{OpenSSH}}
Used to control every server, create encrypted tunnels (autossh),
mount filesystems (sshfs), and remote file transfer (sftp).

\subsection{\href{http://openvpn.net/}{OpenVPN}}
Connects external resources, such as employee mobiles and laptops, to the internal network.

\subsection{\href{http://www.opsview.com/}{Opsview}}
Network monitoring (cf. nagios).

\subsection{\href{http://community.pentaho.com/}{Pentaho}}
Report server, connects to ERP.

\subsection{\href{https://www.piwiki.org/}{Piwik}}
Application to analyze web site traffic.

\href{http://www.mrunix.net/webalizer/}{Webalizer} is used occassionally.

\subsection{\href{https://www.phpbb.com/}{phpBB}}
User discussion forum.

\subsection{\href{http://www.postfix.org/}{Postfix}}
Main SMTP outgoing mail server.

\subsection{\href{http://www.postgresql.org/}{Postgres}}
Database server.

\subsection{\href{http://rsync.samba.org/}{rsync}}
File server.

\subsection{\href{http://www.rsyslog.com/}{rsyslog}}
Logging on every server and workstation.

\subsection{\href{http://www.openbsd.org/cgi-bin/man.cgi/OpenBSD-current/man8/sendmail.8?query=sendmail&sec=8}{sendmail}}
SMTP outgoing mail server, used by default in OpenBSD.

\subsection{\href{http://www.spamassassin.org/}{spamassassin}}
Spam filtering of email.

\subsection{\href{http://fuse.sourceforge.net/sshfs.html}{sshfs}}
Main internal fileserver.

\subsection{\href{http://www.freedesktop.org/wiki/Software/systemd}{systemd}}
System bootup and process manager.

\subsection{\href{http://dnsmasq.org/}{TFTP}}
Network install server.

\subsection{\href{http://vsftpd.beasts.org/}{vsftpd}}
vsftpd FTP server for public facing download and devel servers.

\subsection{\href{http://www.xinetd.org}{xinetd}}
xinetd on Debian systems. inetd on OpenBSD. Misc network utils.

\subsection{\href{http://www.ejabberd.im/}{XMPP/jabber}}
ejabberd, Erlang XMPP (jabber) server.

