%
% IT.
% Information Technology
%
% Aleph Objects Operations Manual
%
% Copyright (C) 2014, 2015 Aleph Objects, Inc.
%
% This document is licensed under the Creative Commons Attribution 4.0
% International Public License (CC BY-SA 4.0) by Aleph Objects, Inc.
%

\section{Servers}
In general, the servers are all running the latest stable release of Debian,
Jessie, version 8, on the amd64 architecture. Some are running Wheezy because
the daemon they hosts prefers it. There is some Debian Squeeze, which is being
migrated. The firewalls are OpenBSD. There is one CentOS and one Fedora
machine.

All machines are backed up at least daily. Updates are run at least weekly,
sooner depending on the nature of the update.

\subsection{Aleph Mountain Servers}
This is a list of servers and nodes that are in the Aleph Mountain building.

\begin{itemize}
\item \texttt{abejas.alephobjects.com} --- Apache, OpenERP.
\item \texttt{amfw1.alephobjects.com} --- OpenBSD, PF, authpf.
\item \texttt{amfw2.alephobjects.com} --- OpenBSD, PF.
\item \texttt{aobuild1.alephobjects.com} --- Compile/build server.
\item \texttt{aocluster1.alephobjects.com} --- 3D Printer cluster Botqueue
       server.
\item \texttt{aodb.alephobjects.com} --- Postgres.
\item \texttt{aogfs1.alephobjects.com} --- Test, potential fileserver.
\item \texttt{aomds1.alephobjects.com} --- Test, potential db server.
\item \texttt{cam.alephobjects.com} --- Motion, Motioneye video camera server.
\item \texttt{jebstation.alephobjects.com} --- sshfs file server.
\item \texttt{tunk.alephobjects.com} --- apt-cacher, OpenVPN server, dnsmasq
      (dhcp, dns cache, tftp), MySQL, OpenLDAP.
\end{itemize}

\subsection{Virtual Servers Elastichosts Los Angeles}
These are machines ``in the cloud''.

\begin{itemize}
\item \texttt{aomail.alephobjects.com} --- Apache, Roundcube.
\item \texttt{analytics.alephobjects.com}  --- Apache, Piwik, MySQL.
\item \texttt{cal.alephobjects.com} --- Calendarserver.
\item \texttt{develdrupal.lulzbot.com} --- Test server. Apache, Drupal,
       Ubercart, MySQL.
\item \texttt{develerp.alephobjects.com} --- Test server. OpenERP, Postgres.
\item \texttt{dodev.alephobjects.com} --- Test server. Odoo, Postgres.
\item \texttt{drupalsql.lulzbot.com} --- MySQL.
\item \texttt{drupalsqlslave.lulzbot.com} --- MySQL, Offline.
\item \texttt{forum.lulzbot.com} --- Apache, phpBB, MySQL.
\item \texttt{jabber.alephobjects.com} --- ejabberd.
\item \texttt{ldap.alephobjects.com} --- OpenLDAP.
\item \texttt{ohai-kit.alephobjects.com} --- Apache, OHAI-Kit, MySQL.
\item \texttt{ops.alephobjects.com} --- Apache, Opsview.
\item \texttt{phplist.alephobjects.com} --- Apache, phplist.
\item \texttt{projects.alephobjects.com} --- Apache, OpenProjects, MySQL.
\item \texttt{survey.alephobjects.com} --- Apache, LimeSurvey.
\item \texttt{thinkup.alephobjects.com} --- Apache, ThinkUp, MySQL, Offline.
\item \texttt{www.lulzbot.com} --- Apache, Drupal, Ubercart.
\item \texttt{www.alephobjects.com} --- Apache, HTML.  :)
\end{itemize}

\subsection{Virtual Servers Elastichosts Dallas}
These are machines ``in the cloud''.

\begin{itemize}
\item \texttt{download.alephobjects.com} --- Apache, vsftpd, rsyncd.
\item \texttt{fone.alephobjects.com} --- Asterisk.
\item \texttt{mail.alephobjects.com} --- Postfix, dovecot, spamassassin, MySQL.
\item \texttt{wiki.alephobjects.com} --- Test server. Apache, Mediawiki, MySQL.
\end{itemize}

\subsection{Tummy Servers}
The CentOS server at Tummy.

\begin{itemize}
\item \texttt{belly1.alephobjects.com} --- Tummy Backup server.
\end{itemize}

